Manuscript Figures for Genome Biology

### 2018-04-30 manuscript_figures/mansuscript_figures.Rmd
Format legends for Fig2; add Fig2

# set up data / results directories
resdir <- "yeast-results"
```

```{r Figure2}
rseed <- 198
sampleSize <- 5
nDE <- 500
resfile <- file.path(resdir, "de5.rds")
de5 <- readRDS(file=resfile)
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

# Figure 2A: Not all methods control FDR at nominal alpha level
p1 <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

# Figure 2B: TPR of methods across nominal alpha level
p2 <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

# Figure 2C: Total number of discoveries varied across method
p3 <- plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

# Figure 2D: Some methods are tailored to detecting smaller effect sizes
p4 <- covariateHeatmap(de5, alpha=0.05, covname="log2FC", trans="log1p")

# maybe 2E? 
# p5 <- aggupset(de5, alpha=ualpha, supplementary = FALSE, return_list = FALSE)

# Figure 2 (ALL)
plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 25)
```

>>>>

# set up data / results directories
resdir <- "yeast-results"
outdir <- "yeast-figs"
dir.create(outdir, showWarnings = FALSE)
```

```{r Figure2}
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")
resfile <- file.path(resdir, "de5.rds")
de5 <- readRDS(file=resfile)
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))

# Figure 2A: Not all methods control FDR at nominal alpha level
p1 <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none")

# Figure 2B: TPR of methods across nominal alpha level
p2 <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none")

# Figure 2C: Total number of discoveries varied across method
p3 <- plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none")

# Figure 2D: Some methods are tailored to detecting smaller effect sizes
p4 <- covariateLinePlot(de5, alpha=0.05, covname="log2FC", trans="log1p",
                        nbins=25)
leg <- get_legend(p4)
p4 <- p4 + theme(legend.position="none")

# maybe 2E? - doesn't return a ggplot object :( 
# fails to convert using ggplotify package
aggupset(de5, alpha=0.05, supplementary = FALSE, 
                       return_list = FALSE)

# Figure 2 (ALL)
Fig2 <- plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))
#Fig2 <- plot_grid(Fig2, p5, ncol=1, rel_heights = c(1, 0.5),
#                 labels = c("", "E"), label_size = 20)
Fig2
ggsave(file.path(outdir, "Figure2.pdf"), width=10, height=8)
```

This is a side-by-side figure displaying the TPR by alpha cutoff, faceted by 
whether the method uses multiple pieces of information or just one (the p-value).
This figure uses the same data as Figure 1.

```{r, Figure3}
# Figure 3: TPR of methods using by pieces of information used 
Fig3 <- plotsim_average(res5d, met="TPR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, facetMethodType = TRUE)

Fig3
ggsave(file.path(outdir, "Figure3.pdf"), width=8, height=4)
```

# Figure 4

This is a heatmap of methods by case studies with color representing the ranking
by of number of rejections @ FDR cutoff 0.05.

```{r, Figure 4}
# TO DO
```

# Figure 5

This is a multi-panel Figure displaying examples of covariate line plots in the
case studies.

```{r, Figure 5}
# TO DO
```

# Figure 6

This is a multi-panel Figure displaying examples of covariate vs p-value scatterplots
and/or histograms in the case studies. 
It will be used to discuss how we evaluated the use of the 
covariates as independent and informative in the case studies.

```{r, Figure 6}
# TO DO
```
